---
title: "Exercise2"
author: "Ziqi Zhu"
date: format(Sys.time(), "%d %B %Y")
format: html
---

```{r}
library(AER)
library(future)
library(gitcreds)
library(knitr)
library(lintr)
library(renv)
library(reprex)
library(styler)
library(tictoc)
library(tidyverse)
library(tinytex)
library(usethis)
```
echo: This controls whether the code itself is included in the document. For instance, #| echo: false would mean the code will be run and its output will show, but the code itself would not be included in the document.
include: This controls whether the output of the code is included in the document. For instance, #| include: false would run the code, but would not result in any output, and the code itself would not be included in the document.
eval: This controls whether the code should be included in the document. For instance, #| eval: false would mean that the code is not run, and hence there would not be any output to include, but the code itself would be included in the document.
warning: This controls whether warnings should be included in the document. For instance, #| warning: false would mean that warnings are not included.
message: This controls whether messages should be included in the document. For instance, #| message: false would mean that messages are not included in the document.
```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(AER)

data("DoctorVisits", package = "AER")

DoctorVisits |>
  ggplot(aes(x = visits)) +
  geom_histogram(stat = "count")
```